---
output: github_document
---

# RSlovakia

This is work in progress to download a set of shapefiles relevant to Slovakia. It was inspired by the popular [RCzechia](https://github.com/jlacko/RCzechia) package for Czech Republic datasets which was in turn inspired by the [tigris](https://github.com/walkerke/tigris) package.

## The following points of interest are currently included:

* Borders
* Regions
* Counties
* Waterways (Rivers and Lakes)
* Roads
* Railroads
* Airports

#### Planning to add the following points of interest during development:

* Population and demographics
* Physical geography such as elevation, forests, etc.
* Points of interest such as parks, churches, schools, government buildings, etc.
* Development, education, health, transport, etc. indicators

## Demo of current functionality

Here is a walkthrough of the current functionality of the package.

```{r, echo = FALSE, warning = FALSE, message = FALSE}

library(RSlovakia)
library(sf)
library(ggplot2)

```

### Borders (Hranice)

```{r, echo = FALSE, warning = FALSE}

borders <- hranice()
ggplot2::ggplot(data = borders) +
  geom_sf() +
  theme_minimal() +
  labs(title = "Slovakia", subtitle = "National borders: hranice()")

```

### Regions (Kraje)

```{r, echo = FALSE, warning = FALSE, message = FALSE}

regions <- kraje()
ggplot2::ggplot(data = regions) +
  geom_sf() +
  geom_sf_label(mapping = aes(label = kraj)) +
  theme_minimal() +
  labs(title = "Slovakia", subtitle = "Regions: kraje()") +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank()
        )
  
```

### Counties (Okresy)

```{r, echo = FALSE, warning = FALSE}

counties <- okresy()
ggplot2::ggplot(data = counties) +
  geom_sf(aes(fill = kraj)) +
  theme_minimal() +
  labs(title = "Slovakia", subtitle = "Counties: okresy()")

```

### Roads (Cesty)

```{r, echo = FALSE, warning = FALSE}

roads <- cesty()
borders <- hranice()
ggplot2::ggplot() +
  geom_sf(data = borders) +
  geom_sf(data = roads, aes(color = oddelovac)) +
  theme_minimal() +
  labs(title = "Slovakia", subtitle = "Roads: cesty()")

```

### Railroads (Zeleznice)

```{r, echo = FALSE, warning = FALSE}

rails <- zeleznice()
borders <- hranice()
ggplot2::ggplot() +
  geom_sf(data = borders) +
  geom_sf(data = rails, aes(color = prevadzkova)) +
  theme_minimal() +
  labs(title = "Slovakia", subtitle = "Railroads: zeleznice()")

```

### Rivers and Lakes and Inland Water (Rieky)

```{r, echo = FALSE, warning = FALSE}

rivers <- rieky()
lakes <- jazera()
borders <- hranice()
ggplot2::ggplot() +
  geom_sf(data = borders) +
  geom_sf(data = rivers, color = "blue", alpha = 0.3) +
  geom_sf(data = lakes, fill = "blue") +
  theme_minimal() +
  labs(title = "Slovakia", subtitle = "Rivers and Lakes and Inland Water: rieky() and jazera()")

```

### Points of Interest - Airports (Letiska)

```{r, echo = FALSE, warning = FALSE}

borders <- hranice()
airports <- letiska()
airports$type <- factor(airports$type, levels = c("small_airport", "medium_airport", "large_airport", "closed"))
ggplot2::ggplot() +
  geom_sf(data = borders) +
  geom_point(data = subset(airports, !type == "closed"), aes(x = longitude_deg, y = latitude_deg, size = type, alpha = type)) +
  theme_minimal() +
  labs(title = "Slovakia", subtitle = "Airports: letiska()", alpha = "Airport Type", size = "Airport Type") +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank()) +
  scale_size_discrete(labels = c("Small", "Medium", "Large")) +
  scale_alpha_discrete(labels = c("Small", "Medium", "Large"))
  

```
