---
output: github_document
---

# RSlovakia

This is work in progress to download a set of shapefiles relevant to Slovakia. It was inspired by the popular [RCzechia](https://github.com/jlacko/RCzechia) package for Czech Republic datasets which was in turn inspired by the [tigris](https://github.com/walkerke/tigris) package.

## The following spatial objects are planned to be included:

* Borders of Slovakia [DONE]
* Regions of Slovakia [DONE]
* Counties of Slovakia [DONE]
* Municipalities of Slovakia
* City parts of cities with defined parts in Slovakia
* Waterways of Slovakia
* Roads of Slovakia [DONE]
* Railroads of Slovakia [DONE]
* Protected natural areas of Slovakia
* Forests of Slovakia
* Terrain of Slovakia

## Demo of current functionality

Here is a walkthrough of the current functionality of the package.

```{r, echo = FALSE, warning = FALSE}

library(RSlovakia)
library(sf)
library(ggplot2)

```

### Borders (Hranice)

```{r, echo = FALSE, warning = FALSE}

borders <- hranice()
ggplot2::ggplot(data = borders) +
  geom_sf() +
  theme_minimal() +
  labs(title = "Slovakia", subtitle = "National borders: hranice()")

```

### Regions (Kraje)

```{r, echo = FALSE, warning = FALSE}

regions <- kraje()
ggplot2::ggplot(data = regions) +
  geom_sf() +
  geom_sf_label(aes(label = kraj))
  theme_minimal() +
  labs(title = "Slovakia", subtitle = "Regions: kraje()")

```

### Counties (Okresy)

```{r, echo = FALSE, warning = FALSE}

counties <- okresy()
ggplot2::ggplot(data = counties) +
  geom_sf(aes(fill = kraj)) +
  theme_minimal() +
  labs(title = "Slovakia", subtitle = "Counties: okresy()")

```

### Roads (Cesty)

```{r, echo = FALSE, warning = FALSE}

roads <- cesty()
borders <- hranice()
ggplot2::ggplot() +
  geom_sf(data = borders) +
  geom_sf(data = roads, aes(color = oddelovac)) +
  theme_minimal() +
  labs(title = "Slovakia", subtitle = "Roads: cesty()")

```

### Railroads (Zeleznice)

```{r, echo = FALSE, warning = FALSE}

rails <- zeleznice()
borders <- hranice()
ggplot2::ggplot() +
  geom_sf(data = borders) +
  geom_sf(data = rails, aes(color = prevadzkova)) +
  theme_minimal() +
  labs(title = "Slovakia", subtitle = "Railroads: zeleznice()")

```

Currently, all of the data is being downloaded and transformed from [diva-gis.org](http://www.diva-gis.org/gdata).
